Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-02 paper/paper.tex
pass on section 2

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the anomaly has
been detected in the execution of the test code or its harness. The
rationale is that the test in this group executed without violating
any internal checks of the API. In constrast, warnings in the
``\lo{}'' group reflect the cases where the anomaly was observed
during the execution of functions not related to the test itself. We
found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another and that is
acceptable.  In those cases, our infrastructure would observe a
discrepancy that is more likely to be associated with an invalid input
produced by the fuzzer, \ie{}, a bug in the test not the
code. Although we did find real bugs from ``\lo{}'' warnings, the
proportion was much lower compared to the ``\hi{}'' warnings. Overall,
only \Fix{12\%} of the reals bugs we found originated from ``\lo{}''
warnings.

>>>>

Recall that a warning can be results of various causes other than a
bug (see Table~\ref{tab:false-positives}). To facilitate inspection,
the infrastructure groups and prioritize these warnings. Considering
prioritization, we classified warnings in two kinds, reflecting their
likelihood to manifest a real bug. Warnings of the kind ``\hi{}'' are
associated with the cases where the anomaly has been detected in the
execution of the test code or its harness. The rationale is that the
test in this group executed without violating any internal checks of
the API. In constrast, warnings in the ``\lo{}'' group reflect the
cases where the anomaly was observed during the execution of functions
not related to the test itself. We found that different engines often
check pre-conditions of those functions differently. It can happen,
for example, that one engine enforces a weaker pre-condition compared
to another and that is acceptable.\Mar{example!} In those cases, our
infrastructure would observe a discrepancy that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
a bug in the test not the code. Although we did find real bugs from
``\lo{}'' warnings, the proportion was much lower compared to
``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
found originated from ``\lo{}'' warnings.
